---
title: "Week 10 Task"
author: "Polisma Yadav"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:  
    keep_md: true
    toc: true
    toc_float: true
    code_folding: hide
    fig_height: 6
    fig_width: 12
    fig_align: 'center'
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r load_libraries, include=FALSE}
# Use this R-Chunk to load all your libraries!
#install.packages("tidyverse") # run this line once in console to get package
library(tidyverse)
library(tidyquant)
library(patchwork)
library(gridExtra)

```

```{r load_data}
# Use this R-Chunk to import all your datasets!

stock_returns_monthly <- c("TSLA", "JMIA", "AAPL") %>%
    tq_get(get  = "stock.prices",
           from = "2020-10-01",
           to   = "2021-11-16") %>%
    group_by(symbol) %>%
    tq_transmute(select     = adjusted, 
                 mutate_fun = periodReturn, 
                 period     = "daily", 
                 col_rename = "Ra")

baseline_returns_monthly <- "XLK" %>%
    tq_get(get  = "stock.prices",
           from = "2020-10-01",
           to   = "2021-11-16") %>%
    tq_transmute(select     = adjusted, 
                 mutate_fun = periodReturn, 
                 period     = "monthly", 
                 col_rename = "Rb")

TSLA <- tq_get("TSLA", get = "stock.prices", from = "2020-10-01", to = "2021-11-12") %>%
  select(symbol, date, adjusted)
end <- as_date("2021-11-12")

AAPL <- tq_get("AAPL", get = "stock.prices", from = "2020-10-01", to = "2021-11-12") %>%
  select(symbol, date, adjusted)
end <- as_date("2021-11-12")

```

## Background

The stock market is overflowing with data. There are many packages in R that allow us to get quick access to information on publicly traded companies. Imagine that you and a friend each purchased about $1,000 of stock in three different stocks at the start of October last year, and you want to compare your performance up to this week. Use the stock shares purchased and share prices to demonstrate how each of you fared over the period you were competing (assuming that you did not change your allocations).

## Data Wrangling

```{r tidy_data}
# Use this R-Chunk to clean & wrangle your data!

stock_returns_monthly_multi <- stock_returns_monthly %>%
    tq_repeat_df(n = 2)
stock_returns_monthly_multi



weights <- c(
    0.50, 0.25, 0.25,
    0.20, 0.20, 0.60
)
stocks <- c("TSLA", "JMIA", "AAPL")
weights_table <-  tibble(stocks) %>%
    tq_repeat_df(n = 2) %>%
    bind_cols(tibble(weights)) %>%
    group_by(portfolio)
weights_table

```

```{r}

portfolio_returns_monthly_multi <- stock_returns_monthly_multi %>%
    tq_portfolio(assets_col  = symbol, 
                 returns_col = Ra, 
                 weights     = weights_table, 
                 col_rename  = "Ra")
portfolio_returns_monthly_multi




RaRb_multiple_portfolio <- left_join(portfolio_returns_monthly_multi, 
                                     baseline_returns_monthly,
                                     by = "date")
RaRb_multiple_portfolio




RaRb_multiple_portfolio %>%
    tq_performance(Ra = Ra, Rb = Rb, performance_fun = table.CAPM)



RaRb_multiple_portfolio %>%
    tq_performance(Ra = Ra, Rb = NULL, performance_fun = SharpeRatio)
```

```{r}
p1 <- TSLA %>%
ggplot(aes(x = date, y = adjusted, color = symbol)) +
  geom_smooth(method = loess, formula = y ~ x, se = FALSE) +
  facet_wrap(~ symbol) +
  scale_color_manual(values = c("red")) + 
  theme_bw() +
  theme(legend.position = "none")
p2 <- AAPL %>%
ggplot(aes(x = date, y = adjusted, color = symbol)) +
  geom_smooth(method = loess, formula = y ~ x, se = FALSE) +
  facet_wrap(~ symbol) +
  scale_color_manual(values = c("blue")) + 
  theme_bw() +
  theme(legend.position = "none")


```

## Data Visualization
1. 50% TSLA, 25% JMIA, 25% AAPL
2. 20% TSLA, 20% JMIA, 60% AAPL

```{r}
portfolio_growth_monthly_multi <- stock_returns_monthly_multi %>%
    tq_portfolio(assets_col   = symbol, 
                 returns_col  = Ra, 
                 weights      = weights_table,
                 col_rename   = "investment.growth",
                 wealth.index = TRUE) %>%
    mutate(investment.growth = investment.growth * 1000)
```

```{r}
portfolio_growth_monthly_multi %>%
    ggplot(aes(x = date, y = investment.growth, color = factor(portfolio))) +
    geom_line(size = 2) +
    labs(title = "Portfolio Growth",
         subtitle = "Comparing Black(My Portfolio) VS Red(My Friend's)",
         x = "", y = "Portfolio Value",
         color = "Portfolio") +
    geom_smooth(method = "loess", formula = "y ~ x") +
    theme_tq() +
    scale_color_tq() +
    scale_y_continuous(labels = scales::dollar)

grid.arrange(p1, p2, ncol = 2, nrow = 1)

```

## Conclusions

In the graph we can clearly see that My portfolio made better returns than my friend's. I invested most of my money on TSLA stocks and at the end I ended up making slight more profit than Her portfolio which consists of more than 50% of AAPL stocks and less of TSLA. At the end TSLA turned out to be the stock that decided who made better profit and helped me win the competition. I have attached the comparision of AAPL and TSLA stocks to show how TSLA made better profits.
